An equivalence of compositional frameworks

### 2019-04-25 EquivCompFrameworks_20180911kc.tex
initial work on proof

\section*{Various issues-in-progress}
{\chris If Kenny likes, we can use this as a section for all the current issues that need to be resolved, or what we are currently working on or something!}
\begin{itemize}
\item {\chris I think structured cospans should be introduced/recalled way earlier! This is a paper that compares the two,
and both should be presented early.} Sure, I'm fine with that. What section do you think we should bring it up in, or maybe create a new section entirely to mention it? {\chris I think a new section right before that equivalence section would be great!}
\item {\chris Discuss the name of Decorated and Structured cospan double categories one last time? :)}
\end{itemize}

@@

{\chris in progress}
\begin{thm}\label{Equiv}
Let $\mathsf{A}$ and $\mathsf{X}$ be categories with finite colimits, and $F \colon(\mathsf{A},+,0) \to (\mathbf{Cat},\times,\mathbf{1})$ a symmetric lax monoidal pseudofunctor. The symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans is equivalent to the symmetric monoidal double category $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans, where $L \colon \mathsf{A} \to \int{F} \cong \mathsf{X}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ by \cref{thm:Grothendieck} under the assumptions of \cref{thm:mainthmDX}.
\end{thm}
\begin{proof}
To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathsf{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $F\mathbb{C}\textnormal{sp}$ have objects and morphisms of $\mathsf{A}$ as objects and vertical 1-morphisms, respectively. The functor $\mathbb{E}_0$ is trivially an equivalence of categories.

>>>>

\section*{Various issues-in-progress}
{\chris If Kenny likes, we can use this as a section for all the current issues that need to be resolved, or what we are currently working on or something!}
\begin{itemize}
\item {\chris I think structured cospans should be introduced/recalled way earlier! This is a paper that compares the two,
and both should be presented early.} Sure, I'm fine with that. What section do you think we should bring it up in, or maybe create a new section entirely to mention it? {\chris I think a new section right before that equivalence section would be great!}
\item {\chris Discuss the name of Decorated and Structured cospan double categories one last time? :)}
\item {\chris I'm starting a few macros to help us write faster and adjust accordingly if we need to later. On that note, could Kenny `clean' the preamble at some point? I.e. erase the commands not used here, to make it easier to navigate? I would do it but I wouldn't want to erase something you use!}
\end{itemize}

@@

\begin{thm}\label{Equiv}
Let $\mathsf{A}$ and $\mathsf{X}$ be categories with finite colimits, and $F \colon(\mathsf{A},+,0) \to (\mathbf{Cat},\times,\mathbf{1})$ a symmetric lax monoidal pseudofunctor. The symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$ of decorated cospans is equivalent to the symmetric monoidal double category $_{L_F} \mathbb{C}\textnormal{sp}(\mathsf{X})$ of structured cospans, where $L_F \colon \mathsf{A} \to \int{F}$ is the left adjoint of the induced Grothendieck opfibration $\U_F\colon \int{F} \to \mathsf{A}$ by \cref{thm:Grothendieck} under the assumptions of \cref{thm:mainthmDX}.
\end{thm}
\begin{proof}
As explained in (ref), the double category of decorated cospans $\dcsp{F}$ has $\A$ as its category of objects and vertical 1-morphisms, whereas horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $d\in F(c)$ and 2-morphisms are cospan maps $k\colon c\to c'$ such that $(Fk)(d)=d'$.

The symmetric lax monoidal pseudofunctor $F$ corresponds, under the (monoidal) Gro\-the
-ndieck construction, to an opfibration $U_F\colon\int{F}\to\A$ with such and such properties.

{\chris in progress}
To prove this, we define a double functor $\mathbb{E} \colon _L \mathbb{C}\textnormal{sp}(\mathsf{X}) \to F\mathbb{C}\textnormal{sp}$ as follows: the object component of the double functor $\mathbb{E}$ is given by $\mathbb{E}_0 = \id_{\mathsf{A}}$ as both double categories $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ and $F\mathbb{C}\textnormal{sp}$ have objects and morphisms of $\mathsf{A}$ as objects and vertical 1-morphisms, respectively. The functor $\mathbb{E}_0$ is trivially an equivalence of categories.
